systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-07-03 paper/trunk/systemfit_code.tex
added section "Overlap with other functions and packages in R"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@786 591db2bd-e0a0-4d22-8c19-2192dbb7da31

>>>>

\subsection[Overlap with other functions and packages in R]
   {Overlap with other functions and packages in \proglang{R}}

Single-equation models can be fitted in \proglang{R}
by OLS with function \code{lm} (package \pkg{stats})
and by 2SLS with function \code{tsls}
(package \pkg{sem}, \citealp{r-sem-0.9-8}).
This is also possible with the \code{systemfit} function,
but \code{systemfit} is specialized in estimating systems of equation,
i.e.\ more than one equation.
Its capability to estimate single-equation models is just a side-effect.

Function \code{sem} (package \pkg{sem}, \citealp{r-sem-0.9-8})
can be used to estimate structural equation models in \proglang{R}
by Full Information Maximum Likelihood (FIML)
assuming multinormal errors.
A special feature of this function is the estimation
of models with unobserved (°latent°) variables,
which is not possible with \code{systemfit}.
While \code{sem} cannot be used to consistently estimate
systems of simultaneous equations with some endogenous regressors,
it can be used to estimate systems of equations,
where all regressors are exogenous.
However, the latter is rather cumbersome.
Hence, \code{systemfit} is the only function in \proglang{R}
that can be used to estimate systems of simultaneous equations
and it is the most convenient function to estimate
systems of equations with purely exogenous regressors.
